Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-14 manuscript/manuscript.tex
Remove tensor components from Appendix

The gradient and the Marussi tensor of potentials that
depends solely on $r$ have only a few non zero components: the vertical
component of the gradient ($g_z$) and the diagonal components of the
tensor ($g_{xx}$, $g_{yy}$, $g_{zz}$).
Following \citet{Grombein2013}:

@@

\begin{equation}
    g_{xx}(r) = g_{yy}(r) = -\frac{V_\text{sh}(r)}{r^2},
\end{equation}

\begin{equation}
    g_{zz}(r) = \frac{2V_\text{sh}(r)}{r^2}.
\end{equation}

>>>>

The gradient of potentials that
depends solely on $r$ have only one non zero components: the vertical
component of the gradient ($g_z$).
Following \citet{Grombein2013}:

@@
